Trajectories

### 2022-09-07 index.qmd
Report to Quarto

$$
\begin{aligned}\nu_{ij} = & \beta_0 +\beta_1\mathrm{Age}_{i} + \beta_2 \mathrm{Freq}_{j} + \beta_3\mathrm{Phon}_{j} + \beta_4\mathrm{Exposure}_{ij} + \beta_5 \mathrm{Levenshtein}_{j} +
\beta_6\mathrm{(Age_{i} \cdot \mathrm{Exposure}_{ij}}) + \beta_7\mathrm{(\mathrm{Age}_{i} \cdot \mathrm{Levenshtein}_{j}}) +  \beta_8\mathrm{(Exposure_{ij} \cdot \mathrm{Levenshtein}_{j}}) + 
\beta_9{(\mathrm{Age}_{i} \cdot \mathrm{Exposure}_{ij} \cdot \mathrm{Levenshtein}_{j}}) +\\

@@

```{r}
#| label: results-raw
#| echo: true
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 4
df %>%
    mutate(
        lv = cut_interval(lv, 5),
        age = floor(age)
    ) %>% 
    count(lv, age, response) %>%
    mutate(prop = n/sum(.$n)) %>% 
    ggplot(aes(age, prop, colour = response, fill = response)) +
    facet_wrap(~lv, nrow = 1) +
    geom_col(position = position_fill()) +
    geom_hline(yintercept = 0.5, colour = "black", size = 0.5) +
    labs(
        x = "Age (months)",
        y = "% responses", 
        colour = "Response",
        fill = "Response"
    ) +
    scale_fill_d3() +
    scale_colour_d3() +
    scale_x_continuous(breaks = seq(0, 40, 2)) +
    scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
    theme(
        legend.position = "top",
        axis.text.y = element_text(size = 7),
        axis.text.x = element_text(size = 7),
        axis.ticks.y = element_blank(),
        panel.grid = element_blank()
    )
```

>>>>

$$\begin{aligned}\nu_{ij} = & \beta_0 +\beta_1\mathrm{Age}_{i} + \beta_2 \mathrm{Freq}_{j} + \beta_3\mathrm{Phon}_{j} + \beta_4\mathrm{Exposure}_{ij} + \beta_5 \mathrm{Levenshtein}_{j} +
\beta_6\mathrm{(Age_{i} \cdot \mathrm{Exposure}_{ij}}) + \beta_7\mathrm{(\mathrm{Age}_{i} \cdot \mathrm{Levenshtein}_{j}}) +  \beta_8\mathrm{(Exposure_{ij} \cdot \mathrm{Levenshtein}_{j}}) + 
\beta_9{(\mathrm{Age}_{i} \cdot \mathrm{Exposure}_{ij} \cdot \mathrm{Levenshtein}_{j}}) +\\

@@

```{r}
#| label: results-raw
#| echo: true
#| message: false
#| warning: false
#| fig-width: 15
#| fig-height: 10
df %>%
    mutate(
        lv = cut_interval(lv, 5),
        age = floor(age)
    ) %>% 
    count(lv, age, response) %>%
    mutate(prop = n/sum(.$n)) %>% 
    ggplot(aes(age, prop, colour = response, fill = response)) +
    facet_wrap(~lv, nrow = 1) +
    geom_col(position = position_fill()) +
    geom_hline(yintercept = 0.5, colour = "black", size = 0.5) +
    labs(
        x = "Age (months)",
        y = "% responses", 
        colour = "Response",
        fill = "Response"
    ) +
    scale_fill_d3() +
    scale_colour_d3() +
    scale_x_continuous(breaks = seq(0, 40, 2)) +
    scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
    theme(
        legend.position = "top",
        axis.text.y = element_text(size = 7),
        axis.text.x = element_text(size = 7),
        axis.ticks.y = element_blank(),
        panel.grid = element_blank()
    )
```
